---
title: "Milestone Four"
author: "Sam Lowry"
date: "2/28/2020"
output: bookdown::pdf_document2
bibliography: bib.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::write_bib(c("book", "maria"), "bib.bib", width = 60)
library(gt)
library(tidyverse)
library(bookdown)
library(gtsummary)
```

# GT Table

This gt table is based upon the National Election Survery data from last class.

```{r data}
#I made a raw data folder and put the data in it and loaded it in.

load("raw-data/nes.rda")

#I cleaned the data the same as we did last class.
nes <- nes %>% 
  select(year, partyid7, real_ideo, race_adj, age_discrete, educ1, female, income) %>% 
  drop_na()
```

```{r gt}
#I then cleaned the data to show the total male and female numbers for a select number of years.
gt_data <- nes %>% 
  filter(year %in% c(1994, 1996, 1998, 2000)) %>% 
  group_by(year) %>%
  summarise(Female = sum(female),
            Male = n() - sum(female),
            Total = n()) %>% 
  rename(Year = year)

#I then made the needed gt plot.
#I had a header but the odd thing is that it would not knit if I had it. 
#A topic for discussion later on. 
gt_data %>% 
  gt() %>% 
  tab_header(title = "Gender by Year",
             subtitle = "National Election Survery")
```

# GT Summary

This gtsummary table shows a regression using female to explain party identification based upon the National Election Survery data from last class. 
```{r regression}
#I then used lm in order to make a model the same as we did in class except with lm because it works with tbl_regression. 
women_model <- glm(partyid7 ~ female, data = nes)

#I made the regression table. 
tbl_regression(women_model)
```
My Github repository for this milestone is in the footnote below. ^[https://github.com/SamuelLowry/gov1006-milestone-4.git]
I used @book and @maria in order to complete this milestone. 

\newpage

# References